Title here

### 2017-01-26 portfolio/text/ms.Rmd
More ms edits

<!-- TODO mention the quadrants in figure 4 -->

Alaskan halibut and sablefish fisheries were converted to individual fishery 
quota (IFQ) management in 1995, which potentially confounds our estimates with a
major regulatory change. Therefore, we refit our models allowing all 
strategy-level effects involving halibut and sablefish permits to vary 
separately before and after the introduction of IFQs. The introduction of IFQs 
was associated with a reduction in revenue variability of ~25% (TODO XX--XX 95%
CI) for individuals with only halibut or sablefish permits (Fig. S\figifq A).
<!-- TODO AH: We need to note that the populatoin changed -->
Furthermore, for individuals within most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\figifq B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\figifq B).

>>>>

<!-- TODO mention the quadrants in figure 4? -->

Alaskan halibut and sablefish fisheries were converted to individual fishery 
quota (IFQ) management in 1995, which potentially confounds our estimates with a
major regulatory change. Therefore, we refit our models allowing all 
strategy-level effects involving halibut and sablefish permits to vary 
separately before and after the introduction of IFQs. The introduction of IFQs 
was associated with a reduction in revenue variability of ~20--30% for
individuals with only halibut or sablefish permits (Fig. S\figifq A).
<!-- TODO AH: We need to note that the populatoin changed -->
Furthermore, for individuals within most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\figifq B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\figifq B).
